Initial report

### 2023-03-18 README.Rmd
updated readme with fig folder description

  * `ecaw_source_raw_preprocessing.Rmd` file contains the code necessary for the transformation of the source data (the datafile downloaded directly from Qualtrics as is) to the raw datafile (datafile with standard naming). We also made sure that the raw datafile does not contain any information that can be used to indetify any of the respondents.
  * `ecaw_raw_processed_preprocessing.Rmd` file contains the code that cleans the dataset and transforms is into tidy format ready for the analysis.

The `manuscript/` folder contains the manuscript and supplementary materials documents with the analysis code embedded in them. The folder also includes the `interactive_report.Rmd` file, which includes an interactive document for reanalysing our results with different subsets of the data. To run the interactive document locally on your computer, click the _Run document_ button in Rstudio or run the `rmarkdown::run(here::here("manuscript/interactive_report.Rmd"))` function in your R console.

>>>>

  * `ecaw_source_raw_preprocessing.Rmd` file contains the code necessary for the transformation of the source data (the datafile downloaded directly from Qualtrics as is) to the raw datafile (datafile with standard naming). We also made sure that the raw datafile does not contain any information that can be used to identify any of the respondents.
  * `ecaw_raw_processed_preprocessing.Rmd` file contains the code that cleans the dataset and transforms is into tidy format ready for the analysis.

The `manuscript/` folder contains the manuscript and supplementary materials documents with the analysis code embedded in them. The folder also includes the `interactive_report.Rmd` file, which includes an interactive document for reanalyzing our results with different subsets of the data. To run the interactive document locally on your computer, click the _Run document_ button in Rstudio or run the `rmarkdown::run(here::here("manuscript/interactive_report.Rmd"))` function in your R console. The `figs/` subfolder contains the rendered figures from the manuscript and supplementary materials in .pdf and .png formats.
